Dynamic Modeling for Optimal Cryptoeconomic Policies

### 2023-11-03 Paper/main.tex
some deterministic math
complete deterministic solution
fix citation year error

\renewcommand \thesection{\Roman{section}}
\renewcommand \thesubsection{\arabic{section}.\arabic{subsection}}

@@

This paper is organized as follows: Section \ref{sec:literature} provides an overview of the established literature. Section \ref{sec:model} outlines the baseline model by \citet{biais2020equilibrium} and replicates its solutions (\ref{sec:baseline}) and outlines the current progress of my extended model (\ref{sec:extensions}). Section \ref{sec:data} describes the data I plan to use for calibration.

\section{Literature Review}
\label{sec:literature}
% TODO: add new William Cong paper
My research is related to the emerging literature on modeling cryptocurrencies and the blockchain economy. Following \citet{yermack2015bitcoin} that argued that Bitcoin is not a currency, there was an interest in studying Bitcoin as a financial asset. \citet{athey2016bitcoin, garratt2018bitcoin, biais2020equilibrium, pagnotta2022decentralizing} studied equilibria in asset pricing models for Bitcoin. \citet{schilling2019some, schilling2019currency} focused on the interactions between Bitcoin and the real economy, including dollar exchange rate and currency substitution. A broader set of models for Bitcoin include \citet{bolt2020value, catalini2020some, hinzen2022bitcoin, chiu2017economics, huberman2021monopoly}. For Proof-of-Stake protocols, \citet{saleh2019volatility, saleh2021blockchain} modeled their general volatility and welfare, while \citet{catalini2020markets} examined their tokenomics in the presence of an attack. A common result of the aforementioned asset pricing models is that static token supply causes all shocks are absorbed by the token price, which explains the high volatility of Bitcoin. This provides the motivation for an endogenous token supply in my model, which adds response mechanisms in terms of dynamic policy rules therefore can potentially mitigate the price effect of exogenous shocks.

@@

\subsection{Baseline model} 
\label{sec:baseline}
This model was proposed by \citeauthor*{biais2020equilibrium} in their 2020 paper in The Journal of Finance titled ``Equilibrium Bitcoin Pricing". Their main idea is that the fundamental value of cryptocurrencies comes from the stream of future transactional benefits (e.g. access to unique goods, not expropriated/taxed/constrained by government, direct internet access). The primary result is that Bitcoin price changes partly due to changes in fundamentals (net transactional benefits) but mostly due to extrinsic volatility.

@@

\subsection{Prices}
% Do we need price data from many exchanges/denominations?
The data set starts on September 16th, 2022, with the implementation of the Merge, and ends on September 31, 2023. I used time series data of daily ETH-USD prices provided by Messari\footnote{\url{https://messari.io/}}. For robustness checks, I follow \cite{biais2020equilibrium} to construct time series based on ETH prices denominated in five different currencies from 20 major exchanges. For non-USD denominations, I converted the prices using daily USD exchange rates data from Federal Reserve Economic Data (FRED).

@@

>>>>

\renewcommand \thesection{\Roman{section}}
\renewcommand \thesubsection{\arabic{section}.\arabic{subsection}}
\setcounter{secnumdepth}{4}

@@

This paper is organized as follows: Section \ref{sec:literature} provides an overview of the established literature. Section \ref{sec:model} outlines the baseline model by \citet{biais2023equilibrium} and replicates its solutions (\ref{sec:baseline}) and outlines the current progress of my extended model (\ref{sec:extensions}). Section \ref{sec:data} describes the data I plan to use for calibration.

\section{Literature Review}
\label{sec:literature}
% TODO: add new William Cong paper
My research is related to the emerging literature on modeling cryptocurrencies and the blockchain economy. Following \citet{yermack2015bitcoin} that argued that Bitcoin is not a currency, there was an interest in studying Bitcoin as a financial asset. \citet{athey2016bitcoin, garratt2018bitcoin, biais2023equilibrium, pagnotta2022decentralizing} studied equilibria in asset pricing models for Bitcoin. \citet{schilling2019some, schilling2019currency} focused on the interactions between Bitcoin and the real economy, including dollar exchange rate and currency substitution. A broader set of models for Bitcoin include \citet{bolt2020value, catalini2020some, hinzen2022bitcoin, chiu2017economics, huberman2021monopoly}. For Proof-of-Stake protocols, \citet{saleh2019volatility, saleh2021blockchain} modeled their general volatility and welfare, while \citet{catalini2020markets} examined their tokenomics in the presence of an attack. A common result of the aforementioned asset pricing models is that static token supply causes all shocks are absorbed by the token price, which explains the high volatility of Bitcoin. This provides the motivation for an endogenous token supply in my model, which adds response mechanisms in terms of dynamic policy rules therefore can potentially mitigate the price effect of exogenous shocks.

@@

\subsection{Baseline model} 
\label{sec:baseline}
This model was proposed by \citeauthor*{biais2023equilibrium} in their 2020 paper in The Journal of Finance titled ``Equilibrium Bitcoin Pricing". Their main idea is that the fundamental value of cryptocurrencies comes from the stream of future transactional benefits (e.g. access to unique goods, not expropriated/taxed/constrained by government, direct internet access). The primary result is that Bitcoin price changes partly due to changes in fundamentals (net transactional benefits) but mostly due to extrinsic volatility.

@@

\subsection{Prices}
% Do we need price data from many exchanges/denominations?
The data set starts on September 16th, 2022, with the implementation of the Merge, and ends on September 31, 2023. I used time series data of daily ETH-USD prices provided by Messari\footnote{\url{https://messari.io/}}. For robustness checks, I follow \cite{biais2023equilibrium} to construct time series based on ETH prices denominated in five different currencies from 20 major exchanges. For non-USD denominations, I converted the prices using daily USD exchange rates data from Federal Reserve Economic Data (FRED).

@@

%--------------------Appendices--------------------
\newpage
\subfile{appendix}
